\clearemptydoublepage
\phantomsection
\addcontentsline{toc}{chapter}{Acknowledgments}	


%\chapter*{Acknowledgements}

\vspace*{2cm}

\begin{center}
{\Large \bf Acknowledgments}
\end{center}

So here it is, my Master's thesis! Despite the fact, that my name is stated as the single author of this work, this document is written in a 'we' formulation. And this has to be taken seriously! This work could not have been realized in the way it is without the help and support of various talented minds.

To begin with, my highest appreciation and biggest 'thank you' belongs to Gennaro Raiola, for his elementary work of bringing the Stack-of-Tasks to life inside PAL Robotics. He was not only a patient colleague, but furthermore became a good friend, who made my time in Barcelona as good as it was.

I want to thank Adolfo Rodr{\'i}guez Tsouroukdissian, who mentored my work inside PAL and guided me through all arising troubles with smart ideas. Equally to J{\"u}rgen Sturm, who took not just care about all academic bureaucracy, but also gave me valuable feedback for designing this work. 

Furthermore, a big thanks goes to Hilario Tom{\'e}, who was patient and compassionated enough to reveal all necessary mathematical myths, I encountered during this work; Paul Mathieu and Bence Magyar for enlightening me with insights of C++ and ROS; Various lovely people all around the globe for cross-reading this document.

Altogether, I want to thank my colleagues at PAL Robotics, who are a great team and make working there as much fun as it could be. 

\vspace{1cm}
